---
title: "Analyses"
author: "Anders Skyrud Danielsen"
date: "12 10 2023"
output: html_document
---

# Setup

```{r setup, echo=T}

# Setup

pacman::p_load(
  survival,
  tidyverse,
  tidylog,
  rio,
  lubridate,
  gtsummary,
  viridis,
  survminer,
  lme4,
  splines,
  EValue,
  patchwork,
  broom
  )

# Load the data

setwd("~/")

study_data2 <- import("study_data2.csv") 

study_data2 <- study_data2 %>% 
  mutate(length_of_stay = replace_na(length_of_stay, 1)) %>% 
  mutate(Charlson_grp = case_when(
    Charlson <3 ~ "<3",
    Charlson >2 & Charlson <6 ~ "3-5",
    TRUE ~ ">5"))

theme_set(theme_minimal())

```

# Analyses

## Table 2

```{r table1} 

study_data2 %>% 
  mutate(diagnosis_year = as.character(diagnosis_year)) %>% 
  mutate(age_cat = factor(age_cat, levels = c("<40 years", "40-49 years", "50-59 years", "60-69 years", "70-79 years", "80-89 years", ">=90 years"))) %>% 
  select(AMR, event, age_at_baseline, age_cat, LinkedSex, type_and_treatment, diagnosis_year, other_primary, polymicrobial, Charlson_grp, length_of_stay, total_positives) %>% 
  tbl_summary(
    by = AMR,
    label = list(
      event ~ "Non-survivor",
      age_at_baseline ~ "Age (continuous)",
      age_cat ~ "Age (categorical)",
      LinkedSex ~ "Sex",
      type_and_treatment ~ "Cancer type and treatment recieved",
      diagnosis_year ~ "Year of cancer diagnosis",
      other_primary ~ "Other primary infection",
      polymicrobial ~ "Polymicrobial bacteraemia",
      Charlson_grp ~ "Charlson Comorbidity Index",
      length_of_stay ~ "Past hospitalisation",
      total_positives ~ "Number of bacteraemias"
    ),
    percent = "row"
  ) %>% 
  add_overall() %>% 
  modify_spanning_header(c("stat_1", "stat_2") ~ "**Resistant infection**") %>% 
  bold_labels()

```

## Table 3

What bug-drug combinations do we have?

```{r bug-drug}

study_data2 %>% 
  select(event, TGCREC:CSEC) %>% 
  tbl_summary(
    by = event,
    missing = "no",
    label = list(
    ),
    percent = "row"
  ) %>% 
  add_overall() %>% 
  modify_spanning_header(c("stat_1", "stat_2") ~ "**Non-survivors**") 

```

## Excess mortality and PAF estimation

### Figure 2

IPTW weighting, with a graphical display of weight distributions.

```{r IPTW}

# Weighting

# Stabilised

model_num <- glm(AMR ~ 1, 
                 data = study_data2, family = binomial)
model_denom <- glm(AMR ~ LinkedSex + age_at_baseline + factor(type_and_treatment) + polymicrobial + factor(Charlson_grp) +
                     factor(diagnosis_year) + other_primary + length_of_stay,
                 data = study_data2, family = binomial)

prob.num <- predict(model_num, study_data2, type="response")
prob.denum <- predict(model_denom, study_data2, type="response")

study_data2$weight <- (study_data2$AMR==1)*prob.num/prob.denum + (study_data2$AMR==0)*(1-prob.num)/(1-prob.denum)

print(summary(study_data2[study_data2$AMR == 0,]$weight))
print(summary(study_data2[study_data2$AMR == 1,]$weight))


# Unstabilised 
#pAgivenL <- ifelse(study_data2$AMR == 0, 1-prob.denum, prob.denum)
#study_data2$weight <- 1/pAgivenL
#print(summary(study_data2$weight))

# Create the mirror histogram plot
mirror_hist_plot <- ggplot(subset(study_data2, AMR == 1), aes(x = weight, fill = factor(AMR))) +
  geom_histogram(aes(y = - ..density..), bins = 30) +
  geom_histogram(data = subset(study_data2, AMR == 0),
                 aes(x = weight, y = ..density.., fill = factor(AMR)), bins = 30, alpha = 0.7) +
  labs(y = "Density (%)", x = "IPWs", fill = "Exposure group") + 
  scale_fill_viridis_d(labels = c("Resistant", "Susceptible")) + 
  theme_classic() +
  guides(fill = guide_legend(title = "Exposure Group"))

# Save the plot
ggsave("figure_2.png", plot = mirror_hist_plot, width = 8, height = 6, units = 'in', dpi = 300)

```

### Figure 3

## Figure 3

Crude survival curves.

```{r survival curves}

# crude survival curves 
study_data2$event <- as.numeric(study_data2$event)

# create a survival object using the Surv function
surv_object <- survfit(Surv(studytime, event) ~ AMR, data = study_data2)

# Export for plotting
surv_data <- tidy(surv_object, conf.int = TRUE) 
write.csv(surv_data, "figure_3A.csv", row.names = FALSE)

```

Weighted survival curves

```{r weighted survival curves}

set.seed(1337)

# Function returning "curves" in step function format 

stepf <- function(dataset) {
  model_num <- glm(AMR ~ 1, data = dataset, family = binomial())
  model_denom <- glm(AMR ~ LinkedSex + age_at_baseline + factor(type_and_treatment) + polymicrobial + factor(Charlson_grp) +
                           factor(diagnosis_year) + other_primary + length_of_stay,
                     data = dataset, family = binomial())
  
  prob.num <- predict(model_num, type = "response")
  prob.denum <- predict(model_denom, type = "response")

  dataset$weight <- (dataset$AMR==1)*prob.num/prob.denum + (dataset$AMR==0)*(1-prob.num)/(1-prob.denum)
  
  dataset1 = dataset[dataset$AMR==0, ]
  km_counterfactual <- survfit(Surv(studytime, event) ~ 1, data = dataset1, weights = weight)
  
  # Extracting survival times and probabilities
  times <- km_counterfactual$time  
  stepfu <- km_counterfactual$surv
  
  # Returning a data frame of times and survival probabilities
  output = data.frame(t=times, stepfu=stepfu)
    
  return(output)
}

# Function for bootstrapping step functions
stepboot <- function(dataset, nboot=50, type="quantile",zerovalue=1, stepf){
  grid <- seq(1, 31, by = 1) # Set time grid
  # Estimate on original data:
  org.fit <- stepf(dataset)
  org.est <- stepfun(org.fit$t,c(zerovalue,org.fit$stepfu),right=T)
  # Create matrix for bootstrap results:
  resmatrix <- matrix(nrow=nboot, ncol=length(grid))
  # Run on bootstrap resamples:
  for(i in 1:nboot){
    #create bootstrap datasets:
    bootids <- sample(unique(rownames(dataset)),replace=T)
    freq.table <- table(factor(bootids,levels=unique(rownames(dataset))))
    bootweights <- as.integer(freq.table[rownames(dataset)])
    dta.boot <- dataset[rep(row.names(dataset), bootweights),]
    #Run analysis on boostrap data:
    fit.boot <- stepf(dta.boot)
    stepf.boot <- stepfun(fit.boot$t,c(zerovalue,fit.boot$stepfu),right=T)
    resmatrix[i,] <- stepf.boot(grid)
  }
  # Quantilie intervals:
  if(type == "quantile"){
    q <- apply(resmatrix, 2, quantile, probs = c(0.025,0.975),  na.rm = FALSE)
  }
  # Return:
  data.frame(t=grid,org.est=org.est(grid),lower=q[1,],upper=q[2,])
}

# Run bootstrap
boots = stepboot(study_data2, nboot=1000, type="quantile", zerovalue=1, stepf=stepf)

# Export for plotting
write.csv(boots, "figure_3C1.csv", row.names = FALSE)

# Kaplan-Meier survival fit with confidence intervals
km_fit <- survfit(Surv(studytime, event) ~ 1, data = study_data2)

# Convert survfit object to a dataframe for plotting
km_data <- tidy(km_fit, conf.int = TRUE) 

# Export for plotting
write.csv(km_data, "figure_3C2.csv", row.names = FALSE)

```

### Excess mortality estimates

```{r excess mortality}

#Estimate the observed CIF:
fit.o <- survfit(Surv(studytime, event) ~ 1, data = study_data2)
# Get the cumulative incidence
cif.o.adj <- 1 - fit.o$surv[length(fit.o$surv)]
#Estimate the counterfactual CIF, assuming everyone had no AMR: 
# Filter the dataset
no_AMR_data <- study_data2[study_data2$AMR == 0, ]
# Fit a weighted survival curve
fit.c.pseudo <- survfit(Surv(studytime, event) ~ 1, data = no_AMR_data, weights = weight)
# Get the cumulative incidence at the last observed time point
cif.c.pseudo <- 1 - fit.c.pseudo$surv[length(fit.c.pseudo$surv)]
excess_mortality <- cif.o.adj - cif.c.pseudo

# Print the results 
print(excess_mortality)

```

Bootstrapping for CI.

```{r bootstrapping excess mortality}

set.seed(1337) # For reproducibility

# Define the function to calculate the weighted excess mortality for a given dataset
calculate_excess_mortality <- function(dataset) {
  # Calculate weights
  model_num <- glm(AMR ~ 1, data = dataset, family = binomial())
  model_denom <- glm(AMR ~ LinkedSex + age_at_baseline + factor(type_and_treatment) + polymicrobial + factor(Charlson_grp) +
                     factor(diagnosis_year) + other_primary + length_of_stay,
                     data = dataset, family = binomial())

  prob.num <- predict(model_num, type = "response")
  prob.denum <- predict(model_denom, type = "response")

  dataset$weight <- ifelse(dataset$AMR == 1, prob.num / prob.denum, (1 - prob.num) / (1 - prob.denum))

  # Estimate the observed CIF with all data
  fit.o <- survfit(Surv(studytime, event) ~ 1, data = dataset)
  cif.o.adj <- 1 - fit.o$surv[length(fit.o$surv)]

  # Estimate the counterfactual CIF, assuming everyone had no AMR
  no_AMR_data <- dataset[dataset$AMR == 0, ]
  fit.c.pseudo <- survfit(Surv(studytime, event) ~ 1, data = no_AMR_data, weights = no_AMR_data$weight)
  cif.c.pseudo <- 1 - fit.c.pseudo$surv[length(fit.c.pseudo$surv)]

  # Calculate and return excess mortality
  excess_mortality <- cif.o.adj - cif.c.pseudo
  return(excess_mortality)
}

# Bootstrap procedure
nboot <- 1000
excess_mortality.boot <- numeric(nboot)

for (i in 1:nboot) {
  # Create a bootstrap dataset
  bootids <- sample(nrow(study_data2), replace = TRUE)
  boot_data <- study_data2[bootids, ]
  
  # Calculate excess mortality for the bootstrap sample
  excess_mortality.boot[i] <- calculate_excess_mortality(boot_data)
}

# Calculate the 95% Confidence Interval for excess mortality
excess_mortality_CI <- quantile(excess_mortality.boot, c(0.025, 0.975))
print(excess_mortality_CI)

```

Dataframe for figure 4.

```{r excess mortality plot}

# Bootstrapped Excess Mortality Estimates
bootstrapped_excess_mortality <- excess_mortality.boot 

# Point Estimate and Confidence Intervals for Excess Mortality
point_estimate_excess_mortality <- excess_mortality 
lower_ci_excess_mortality <- excess_mortality_CI[1] 
upper_ci_excess_mortality <- excess_mortality_CI[2] 

# Create a dataframe for plotting
excess_mortality_data <- data.frame(bootstrapped_excess_mortality)

```

### PAF

First point estimate for in-text referencing. 

```{r PAF}

# Calculate the PAF
PAF <- (cif.o.adj - cif.c.pseudo) / cif.o.adj

# Print the results
cat("PAF due to AMR at the end of follow-up:", PAF, "\n")

```

Bootstrapping for CI.

```{r bootstrapping PAF}

set.seed(1337) # For reproducibility

# Define the function to calculate the weighted excess mortality for a given dataset
calculate_PAF <- function(dataset) {
  
  # Calculate weights
  model_num <- glm(AMR ~ 1, data = dataset, family = binomial())
  model_denom <- glm(AMR ~ LinkedSex + age_at_baseline + factor(type_and_treatment) + polymicrobial + factor(Charlson_grp) +
                     factor(diagnosis_year) + other_primary + length_of_stay,
                     data = dataset, family = binomial())

  prob.num <- predict(model_num, type = "response")
  prob.denum <- predict(model_denom, type = "response")

  dataset$weight <- ifelse(dataset$AMR == 1, prob.num / prob.denum, (1 - prob.num) / (1 - prob.denum))

  # Estimate the observed CIF with all data
  fit.o <- survfit(Surv(studytime, event) ~ 1, data = dataset)
  cif.o.adj <- 1 - fit.o$surv[length(fit.o$surv)]

  # Estimate the counterfactual CIF, assuming everyone had no AMR
  no_AMR_data <- dataset[dataset$AMR == 0, ]
  fit.c.pseudo <- survfit(Surv(studytime, event) ~ 1, data = no_AMR_data, weights = no_AMR_data$weight)
  cif.c.pseudo <- 1 - fit.c.pseudo$surv[length(fit.c.pseudo$surv)]

  # Calculate and return excess mortality
  PAF <- (cif.o.adj - cif.c.pseudo) / cif.o.adj 
  return(PAF)
}

# Bootstrap procedure
nboot <- 1000
PAF.boot <- numeric(nboot)

for (i in 1:nboot) {
  # Create a bootstrap dataset
  bootids <- sample(nrow(study_data2), replace = TRUE)
  boot_data <- study_data2[bootids, ]
  
  # Calculate excess mortality for the bootstrap sample
  PAF.boot[i] <- calculate_PAF(boot_data)
}

# Calculate the 95% Confidence Interval for excess mortality
PAF_CI <- quantile(PAF.boot, c(0.025, 0.975))
print(PAF_CI)

# Bootstrapped PAF estimates
bootstrapped_PAF <- PAF.boot 

# Point estimate and confidence intervals
point_estimate <- PAF
lower_ci <- PAF_CI[1]
upper_ci <- PAF_CI[2]

# Create a dataframe to plot
paf_data <- data.frame(bootstrapped_PAF)


```

### E-value

```{r e-value}

# E-value of the excess mortality estimate

# Convert risk difference to risk ratio
baseline_risk <- cif.c.pseudo
rr <- (baseline_risk + excess_mortality) / baseline_risk

rr_lower <- (baseline_risk + excess_mortality_CI[1]) / baseline_risk
rr_upper <- (baseline_risk + excess_mortality_CI[2]) / baseline_risk

# Calculate the E-value 
e_val <- evalue(RR(rr), lo = rr_lower, hi = rr_upper)

print(e_val)

```

### Figure 4

```{r density plots}

excess_mortality_density_plot <- ggplot(excess_mortality_data, aes(x = bootstrapped_excess_mortality)) +
  geom_density(fill = "#440154", alpha = 0.7) +  # Adjust alpha here
  geom_vline(xintercept = point_estimate_excess_mortality, color = "#440154", linetype = "dashed", linewidth = 1) +  # Adjust alpha
  geom_vline(xintercept = lower_ci_excess_mortality, color = "#440154", linetype = "dashed", linewidth = 1, alpha = 0.7) +  # Adjust alpha
  geom_vline(xintercept = upper_ci_excess_mortality, color = "#440154", linetype = "dashed", linewidth = 1, alpha = 0.7) +  # Adjust alpha
  scale_x_continuous(limits = c(0.0, 0.035), breaks = seq(0.0, 0.035, by = 0.005)) +
  labs(title = "A", x = "Excess mortality", y = "Density") +
  theme_classic(base_size = 12) +
  theme(legend.position = "none", plot.caption = element_blank())

PAF_density_plot <- ggplot(paf_data, aes(x = bootstrapped_PAF)) +
  geom_density(fill = "#440154", alpha = 0.7) +  # Adjust alpha here
  geom_vline(xintercept = point_estimate, color = "#440154", linetype = "dashed", linewidth = 1) +  # Adjust alpha
  geom_vline(xintercept = lower_ci, color = "#440154", linetype = "dashed", linewidth = 1, alpha = 0.7) +  # Adjust alpha
  geom_vline(xintercept = upper_ci, color = "#440154", linetype = "dashed", linewidth = 1, alpha = 0.7) +  # Adjust alpha
  scale_x_continuous(limits = c(0.0, 0.125), breaks = seq(0.0, 0.125, by = 0.02)) +
  labs(title = "B", x = "Population-attributable fraction", y = "Density") +
  theme_classic(base_size = 12) +
  theme(legend.position = "none", plot.caption = element_blank())

# Combine the plots vertically 
combined_plot <- excess_mortality_density_plot / PAF_density_plot

# Save the combined plot as a PNG file
ggsave("figure_4.png", plot = combined_plot, device = "png", width = 7, height = 12, units = "in")

```

### Supplementary Material S4

```{r Supplementary Material S4}

# Filter the dataset for pathogen cases only
TGCREC_data <- subset(study_data2, (TGCREC == 1 | TGCSEC == 1))
MRSA_data <- subset(study_data2, (MRSA == 1 | MSSA == 1))
CRPA_data <- subset(study_data2, (CRPA == 1 | CSPA == 1))
TGCRKP_data <- subset(study_data2, (TGCRKP == 1 | TGCSKP == 1))
CRA_data <- subset(study_data2, (CRA == 1 | CSA == 1))
CRKP_data <- subset(study_data2, (CRKP == 1 | CSKP == 1))
vre_data <- subset(study_data2, (VRE == 1 | VSE == 1))
CREC_data <- subset(study_data2, (CREC == 1 | CSEC == 1)) 

set.seed(1337) # Ensure reproducibility

# Function to calculate excess mortality for a given dataset already exists 

# Generalized bootstrap function
bootstrap_excess_mortality <- function(data, nboot = 1000) {
  boot_excess_mortality <- numeric(nboot)
  
  for (i in 1:nboot) {
    boot_data <- data[sample(nrow(data), replace = TRUE), ]
    boot_excess_mortality[i] <- calculate_excess_mortality(boot_data)
  }
  
  CI <- quantile(boot_excess_mortality, c(0.025, 0.975))
  list(mean = mean(boot_excess_mortality), CI_lower = CI[1], CI_upper = CI[2])
}

# Apply bootstrapping to each drug-pathogen combination
pathogen_combinations <- list(TGCREC = TGCREC_data, MRSA = MRSA_data, CRPA = CRPA_data, TGCRKP = TGCRKP_data,
                              CRA = CRA_data, CRKP = CRKP_data, VRE = vre_data, CREC = CREC_data)

results <- lapply(names(pathogen_combinations), function(pathogen) {
  data <- pathogen_combinations[[pathogen]]
  bootstrap_results <- bootstrap_excess_mortality(data)
  c(Pathogen = pathogen, Excess_Mortality = bootstrap_results$mean, 
    CI_Lower = bootstrap_results$CI_lower, CI_Upper = bootstrap_results$CI_upper)
})

# Convert the results to a data frame
results_df <- do.call(rbind, results)
row.names(results_df) <- NULL

# Print the final table
print(results_df)


```

### Sensitivity analysis

```{r sensitivity analysis}

# Weighting

# Stabilised

model_num <- glm(AMR ~ 1, 
                 data = study_data2, family = binomial)
model_denom <- glm(AMR ~ LinkedSex + age_at_baseline + factor(type_and_treatment) + polymicrobial + factor(Charlson_grp) +
                     factor(diagnosis_year) + other_primary + length_of_stay + previous_antibiotics_days,
                 data = study_data2, family = binomial)

prob.num <- predict(model_num, study_data2, type="response")
prob.denum <- predict(model_denom, study_data2, type="response")

study_data2$weight <- (study_data2$AMR==1)*prob.num/prob.denum + (study_data2$AMR==0)*(1-prob.num)/(1-prob.denum)

print(summary(study_data2$weight))

#Estimate the observed CIF:
fit.o <- survfit(Surv(studytime, event) ~ 1, data = study_data2)
# Get the cumulative incidence
cif.o.adj <- 1 - fit.o$surv[length(fit.o$surv)]
#Estimate the counterfactual CIF, assuming everyone had no AMR: 
# Filter the dataset
no_AMR_data <- study_data2[study_data2$AMR == 0, ]
# Fit a weighted survival curve
fit.c.pseudo <- survfit(Surv(studytime, event) ~ 1, data = no_AMR_data, weights = weight)
# Get the cumulative incidence at the last observed time point
cif.c.pseudo <- 1 - fit.c.pseudo$surv[length(fit.c.pseudo$surv)]
excess_mortality <- cif.o.adj - cif.c.pseudo

# Print the results 
print(excess_mortality)

set.seed(1337) # For reproducibility

# Define the function to calculate the weighted excess mortality for a given dataset
calculate_excess_mortality <- function(dataset) {
  # Calculate weights
  model_num <- glm(AMR ~ 1, data = dataset, family = binomial())
  model_denom <- glm(AMR ~ LinkedSex + age_at_baseline + factor(type_and_treatment) + polymicrobial + factor(Charlson_grp) +
                     factor(diagnosis_year) + other_primary + length_of_stay + previous_antibiotics_days,
                     data = dataset, family = binomial())

  prob.num <- predict(model_num, type = "response")
  prob.denum <- predict(model_denom, type = "response")

  dataset$weight <- ifelse(dataset$AMR == 1, prob.num / prob.denum, (1 - prob.num) / (1 - prob.denum))

  # Estimate the observed CIF with all data
  fit.o <- survfit(Surv(studytime, event) ~ 1, data = dataset)
  cif.o.adj <- 1 - fit.o$surv[length(fit.o$surv)]

  # Estimate the counterfactual CIF, assuming everyone had no AMR
  no_AMR_data <- dataset[dataset$AMR == 0, ]
  fit.c.pseudo <- survfit(Surv(studytime, event) ~ 1, data = no_AMR_data, weights = no_AMR_data$weight)
  cif.c.pseudo <- 1 - fit.c.pseudo$surv[length(fit.c.pseudo$surv)]

  # Calculate and return excess mortality
  excess_mortality <- cif.o.adj - cif.c.pseudo
  return(excess_mortality)
}

# Bootstrap procedure
nboot <- 1000
excess_mortality.boot <- numeric(nboot)

for (i in 1:nboot) {
  # Create a bootstrap dataset
  bootids <- sample(nrow(study_data2), replace = TRUE)
  boot_data <- study_data2[bootids, ]
  
  # Calculate excess mortality for the bootstrap sample
  excess_mortality.boot[i] <- calculate_excess_mortality(boot_data)
}

# Calculate the 95% Confidence Interval for excess mortality
excess_mortality_CI <- quantile(excess_mortality.boot, c(0.025, 0.975))
print(excess_mortality_CI)

```

### Table S4

```{r table of the weighted population}

# Calculate both unweighted and weighted statistics
stats_df <- study_data2 %>%
  mutate(LinkedSex_numeric = as.numeric(LinkedSex == "M")) %>%
  group_by(AMR) %>%
  summarize(
    # Unweighted means for continuous and dichotomous variables
    age_unweighted_mean = mean(age_at_baseline, na.rm = TRUE),
    sex_unweighted_proportion = mean(LinkedSex_numeric, na.rm = TRUE), 
    other_primary_unweighted_proportion = mean(other_primary, na.rm = TRUE),
    polymicrobial_unweighted_proportion = mean(polymicrobial, na.rm = TRUE),
    LOS_unweighted_mean = mean(length_of_stay, na.rm = TRUE),
    
    # Weighted means for continuous and dichotomous variables
    age_weighted_mean = sum(age_at_baseline * weight) / sum(weight, na.rm = TRUE),
    sex_weighted_proportion = sum(LinkedSex_numeric * weight) / sum(weight, na.rm = TRUE),
    other_primary_weighted_proportion = sum(other_primary * weight) / sum(weight, na.rm = TRUE),
    polymicrobial_weighted_proportion = sum(polymicrobial * weight) / sum(weight, na.rm = TRUE),
    LOS_weighted_mean = sum(length_of_stay * weight) / sum(weight, na.rm = TRUE),
    .groups = 'drop'
    
  ) %>%
  pivot_longer(
    -AMR,
    names_to = "Statistic",
    values_to = "Value"
  )

# Pivot data to have AMR groups as columns and include both unweighted and weighted statistics
stats_wide_df <- stats_df %>%
  pivot_wider(
    names_from = AMR,
    values_from = Value,
    names_prefix = "AMR_"
  )

# Print the wide-format dataframe
print(stats_wide_df)

```

# Conference 

```{r ECCMID 2024, eval=F}

# Oxford Data
oxford_tbl <- study_data2 %>% 
  select(AMR, age_at_baseline, LinkedSex, diagnose_4, Charlson) %>% 
  tbl_summary(
    by = AMR, 
    label = list(
      age_at_baseline ~ "Age",
      LinkedSex ~ "Sex",
      diagnose_4 ~ "Cancer type",
      Charlson ~ "Charlson Comorbidity Index"
    )
  ) %>% 
  add_overall() %>% 
  modify_spanning_header(c("stat_1", "stat_2") ~ "**Oxford**") %>% 
  bold_labels()

# Export Oxford tbl_summary
saveRDS(oxford_tbl, "oxford_tbl_summary.rds")

# Plots with colour scheme for the poster

# Plotting the density plot
PAF_density_plot <- ggplot(paf_data, aes(x = bootstrapped_PAF)) +
  geom_density(fill = "#92c5de", alpha = 0.8) + 
  geom_vline(xintercept = point_estimate, color = "#0571b0", linetype = "dashed", linewidth = 1) +
  geom_vline(xintercept = lower_ci, color = "#92c5de", linetype = "dashed", linewidth = 1) +
  geom_vline(xintercept = upper_ci, color = "#92c5de", linetype = "dashed", linewidth = 1) +
  scale_x_continuous(limits = c(0.0, 0.5), breaks = seq(0.0, 0.5, by = 0.10)) +
  labs(
    title = "Density plot of bootstrapped population-attributable fraction estimates",
    x = "Population-attributable fraction",
    y = "Density",
    caption = "Dashed lines: Middle - Point estimate; Outer - Confidence interval limits"
  ) +
  theme_classic(base_size = 12) +
  theme(legend.position = "none")

# Save the plot to a PDF file
pdf_file_path_2 <- "PAF_density_plot.pdf"
ggsave(pdf_file_path_2, plot = PAF_density_plot, device = "pdf", width = 7, height = 5)

PAF_density_plot

# Plotting the density plot for Excess Mortality
excess_mortality_density_plot <- ggplot(excess_mortality_data, aes(x = bootstrapped_excess_mortality)) +
  geom_density(fill = "#92c5de", alpha = 0.8) + 
  geom_vline(xintercept = point_estimate_excess_mortality, color = "#0571b0", linetype = "dashed", linewidth = 1) +
  geom_vline(xintercept = lower_ci_excess_mortality, color = "#92c5de", linetype = "dashed", linewidth = 1) +
  geom_vline(xintercept = upper_ci_excess_mortality, color = "#92c5de", linetype = "dashed", linewidth = 1) +
  scale_x_continuous(limits = c(0.0, 0.30), breaks = seq(0.0, 0.25, by = 0.05)) +
  labs(
    title = "Density plot of bootstrapped excess mortality estimates",
    x = "Excess mortality",
    y = "Density",
    caption = "Dashed lines: Middle - Point estimate; Outer - Confidence interval limits"
  ) +
  theme_classic(base_size = 12) +
  theme(legend.position = "none")

# Save the plot to a PDF file
pdf_file_path <- "excess_mortality_density_plot.pdf"
ggsave(pdf_file_path, plot = excess_mortality_density_plot, device = "pdf", width = 7, height = 5)

excess_mortality_density_plot

```



